# Conceptos Generales {#intro}

##Derivadas, derivadas parciales y sus implicaciones.

This methods tries to explain the correlation structure of a set of predictor variables using a smaller set o linear combinations of these variables called ***components***, note that *components* are not variables, rather indicators of linear combinations between variables.<br \>
Given a dataset with $m$ variables a set of $k$ linear combinations can be used to represent it (meaning that $k$ contains almost as much information as the $m$ variables), also $k<<m$.


##Funciones de Activación:

###TanH
```{r}
TanHGener <- function(x0){
  (2/(1+exp(-2*x))-1)
}

x <- seq(-5,5,.01)

y <- TanHGener(x)
plot(x,y,
     main = "Tangente Hiperbolica TanH",
     type = "l",
     col = "red",
     lwd = 4)
```

###Softsign
```{r}
softSignGener <- function(x){
  x/(1+abs(x))
}

y1 <- softSignGener(x)

plot(x,y1,
     main = "Softsign",
     type = "l",
     col = "red",
     lwd = 4)
```

###SoftPlus
```{r}
softPlusGener <- function(x){
  log(1+exp(x))
}

y3 <- softPlusGener(x)

plot(x,y3,
     type = "l",
     main = "SoftPlus",
     col = "red",
     lwd = 4)
```


###SoftExponential
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
softExpGener <- function(a,x){
  if (a < 0){
    -1*((log(1-a*(x+a)))/a)
  }
  else {
    if (a == 0){
      x
    }
    else {
      ((exp(a*x)-1)/a)+a
    }
  }
}


y2 <- softExpGener(-1,x)

plot(x,y2,
     main = "SoftExponential",
     type = "l",
     col = "red",
     lwd = 4)
```

###Sinusoid
```{r}
sinusoidalGener <- function(x){
  sin(x)
}

y4 <- sinusoidalGener(x)

plot(x,y4,
     type = "l",
     main = "Sinusoidal",
     col = "red",
     lwd = 4)
```

###Sinc
```{r}
sincGener <- function(x){
 
  xt<-x
  xt[x==0]=1
  xt[x!=0]=sin(x[x!=0])/x[x!=0]
   xt
}

y5 <- sincGener(x)
plot(x,y5,
     type = "l",
     main = "Sinc",
     col = "red",
     lwd = 4)
```

###Scaled exponential linear unit (SELU)
```{r}
seluGener <- function(l,a,x){
  xt<-x
  xt[x<0]=l*a*(exp(x[x<0])-1)
  xt[x>=0]=l*x[x>=0]
  xt
  #if (x < 0){
   # l*a*(exp(x)-1)
  #}
  #else {
   # l * x
  #}
}

y6 <- seluGener(1.0507, 1.67326,x)
plot(x,y6,
     type = "l",
     main = "SELU",
     col = "red",
     lwd = 4)
```

###Rectified Linear Unit (ReLU)
```{r}
ReLUGener <- function(x){
  
  x[x<0]=0
  x
}

y8 <- ReLUGener(x)

plot(x,y8,
     main = "ReLU",
     type = "l",
     col = "red",
     lwd = 4)
```


###Randomized leaky rectified linear unit (RReLU)
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
rreluGener <- function(a,x){
  xt<-x
  xt[x<0]=a*x[x<0]
  xt
}

y9 <- rreluGener(.5,x)

plot(x,y9,
     main = "RReLU",
     type = "ln",
     col = "red",
     lwd = 4)
```


###Parametric Rectified linear unit (PReLU) is just as RReLU

###Logistic (a.k.a Soft Step)
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
logisticGener <- function(x){
  1/(1+exp(x))
}

y10 <- logisticGener(x)

plot(x,y10,
     main = "Logistic",
     type = "ln",
     col = "red",
     lwd = 4)
```


###Leaky rectified linear unit (Leaky ReLU)
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
leakyReluGener <- function(x){
 
  xt<-x
  xt[x<0]=0.01*x[x<0]
   xt
}

y11 <- leakyReluGener(x)

plot(x,y11,
     main = "Leaky ReLU",
     type = "ln",
     col = "red",
     lwd = 4)
```


###Identity
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
identityGener <- function(x){
  x
}

y12 <- identityGener(x)

plot(x,y12,
     main = "Identity",
     type = "ln",
     col = "red",
     lwd = 4)
```


###Gaussian
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
gaussianGener <- function(x){
  exp(-1*x^2)
}

y13 <- gaussianGener(x)

plot(x,y13,
     main = "Gaussian",
     type = "ln",
     col = "red",
     lwd = 4)
```


###Exponential linear unit (ELU)
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
eluGener <- function(a,x){
  
  xt<-x
  xt[x<0]=a*(exp(x[x<0])-1)
  xt
  
}

y14 <- eluGener(1,x)

plot(x,y14,
     main = "Exponential linear unit (ELU)",
     type = "ln",
     col = "red",
     lwd = 4)
```


###Binary Step
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
binaryGener <- function(x){
  
  #temp1<-x
  
  x[x<=0]<-0
  x[x>0]<-1
  
  x
}
  
 
y15 <- binaryGener(x)

plot(x,y15,
     main = "Binary Step",
     type = "ln",
     col = "red",
     lwd = 4)
```


###Bent identity
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
bentGener <- function(x){
  (((sqrt(x^2+1)-1))+(2))+x
}

y16 <- bentGener(x)
plot(x,y16,
     main = "Bent Identity",
     type = "ln",
     col = "red",
     lwd = 4)
```

<!---
###Arc Tan NO JALA
```{r}
arcTanGener <- function(x){
  (1/tan(x))
}

y17 <- arcTanGener(x)

plot(x, y17)
```
